Manuscript analyses

### 2024-01-12 cilta_cel/Manuscript analyses.Rmd
Update code, add tables and plots

Characteristics <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "CHARACTERISTICS AND OUTCOMES ", skip = 1)
Counts <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "COUNTS")
Infections <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "INFECTIONS")
Support <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "SUPPORT")
Pneumo_titers <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "BACTERIAL AND VIRAL TITERS")
Apheresis <- 
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "APHERESIS")
```

@@

  mutate(across(where(is.character), ~ str_replace(., "Unknown|unknown", NA_character_))) %>%
  # Create site variable
  mutate(site = case_when(
    str_detect(pt_identifier, "MCC")               ~ "Moffitt",
    str_detect(pt_identifier, "CCT")               ~ "Stanford",
    str_detect(pt_identifier, "KUMC")              ~ "KUMC",
    str_detect(pt_identifier, "MDA")               ~ "MD Anderson?",
    str_detect(pt_identifier, "Utah")              ~ "Utah"
  )) %>%
  # Suboptimal is NA
  mutate(across(c(#"bm_plasma_cell_percent_at_pre_ld",
                  "high_marrow_burden_50_percent",
                  # contains("normo_hypo_hyper"),
                  contains("fibrosis"),
                  contains("dysplasia"),
                  "b2_microglobulin_day_180"), 
                ~ str_replace(., "Suboptimal", NA_character_))) %>%
  # Are numerical - also remove "Suboptimal"
  mutate(across(c(starts_with("marrow_fibrosis"),
                  starts_with("ldh_")
                  ), 
                ~ as.numeric(.))) %>%
  mutate(across(c("response_to_bridging_chemotherapy"), 
                ~ str_replace(., "Not evaluable", NA_character_))) %>% 
  # Convert 0/1 to No/Yes
  mutate_at(c("infection_yes_1_no_0",
              "severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0",
              # "bm_plasma_cell_percent_at_pre_ld",
              # "high_marrow_burden_50_percent",
              # "ECOG > or = 2? (Yes, No)",
              # deletion_17p_prior_to_car_t_infusion_yes_no,
              # "t_4_14_prior_to_car_t_infusion_yes_no",
              # "t_14_16_prior_to_car_t_infusion_yes_no",
              # "steroid_use_yes_no", "tocilizumab_yes_no", "anakinra_yes_no",
              # "Bridging Therapy (Yes=1, No=0)",
              # "Received alkylating therapy with bridging (Yes=1, No=0)",
              "need_for_g_csf_post_infus_yes_1_no_0",
              "need_for_ivig_yes_1_no_0",
              "cd34_stem_cell_boost_yes_1_no_0",
              "rbc_transfusion_within_30d_post_cart_yes_1_no_0", "plt_transfusion_within_30d_post_cart_yes_1_no_0", 
              "rbc_transfusion_30d_post_cart_yes_1_no_0", "plt_transfusion_30d_post_cart_yes_1_no_0"), 
            ~ case_when(
              . == 1                                              ~ "Yes",
              . == 0                                              ~ "No",
              TRUE                                                ~ NA_character_
            )) %>% 
  # Marrow ----
  mutate(marrow_cellularity_baseline_normo_hypo_hyper = case_when(
    marrow_cellularity_baseline_normo_hypo_hyper == "\"patchy\""                 ~ "hyper",
    TRUE                                                          ~ marrow_cellularity_baseline_normo_hypo_hyper
  )) %>%
  mutate(marrow_cellularity_day_30_normo_hypo_hyper = case_when(
    marrow_cellularity_day_30_normo_hypo_hyper == "aplastic"                    ~ "hypo",
    TRUE                                                          ~ marrow_cellularity_day_30_normo_hypo_hyper
  )) %>%
  # Separate variable cellularity
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Variable"                         ~ "Yes"
  ), .names = "is_variable_{.col}")) %>% 
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Pauci"                            ~ "Hypo",
    . == "Variable"                         ~ NA_character_,
    TRUE                                    ~ .
  ))) %>%

@@

  # Myeloma
  mutate(oligo_or_non_secretory = case_when(
    oligo_or_non_secretory == "Non-Secretory" ~ "Yes",
    oligo_or_non_secretory == "Oligosecretory" ~ "Yes",
    oligo_or_non_secretory == "Unknown" ~ NA_character_,
    TRUE ~ oligo_or_non_secretory
  )) %>%
  # mutate(oligo_or_non_secretory_yes_no = case_when( # is "oligo_or_non_secretory_yes_no" now
  #   `Yes, Oligo or Yes, Non-Secretory` == "Non-Secretory" ~ "Yes",
  #   `Yes, Oligo or Yes, Non-Secretory` == "Oligosecretory" ~ "Yes",
  #   `Yes, Oligo or Yes, Non-Secretory` == "Oligo-secretory" ~ "Yes",
  #   TRUE ~ `Yes, Oligo or Yes, Non-Secretory`
  # )) %>%
  mutate(subtype = case_when(
    oligo_or_non_secretory_yes_no == "Yes" ~ "Oligo/non-secretory",
    myeloma_involved_heavy_chain == "None (Light Chain Restricted)" | 
     myeloma_involved_light_chain == "Lambda" & 
      is.na(myeloma_involved_heavy_chain) ~ "Light chain only",
    myeloma_involved_heavy_chain != "None (Light Chain Restricted)" 
                   ~ "Intact immunoglobulin (Heavy + Light)",
    TRUE           ~ NA_character_ 
  )) %>%
  # Cytogenetics ----
  mutate(cytogenetics = case_when(
    deletion_17p_prior_to_car_t_infusion_yes_no == "Yes" | 
      t_4_14_prior_to_car_t_infusion_yes_no == "Yes" | 
      t_14_16_prior_to_car_t_infusion_yes_no == "Yes"             ~ "Yes",
    deletion_17p_prior_to_car_t_infusion_yes_no == "No" &
      t_4_14_prior_to_car_t_infusion_yes_no == "No" &
      t_14_16_prior_to_car_t_infusion_yes_no == "No"               ~ "No",
    TRUE                                                           ~ NA_character_
  )) %>%

  # Refractory status ----
  mutate(lenalidomide_exposed_vs_refractory_vs_not_exposed = case_when(
    str_detect(
      lenalidomide_exposed_vs_refractory_vs_not_exposed, "Ref")     ~ "Refractory",
    TRUE           ~ lenalidomide_exposed_vs_refractory_vs_not_exposed
  )) %>% 
  mutate(immuno = case_when(
    lenalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" |
      pomalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory"           ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(proteasome = case_when(
    bortezomib_exposed_vs_refractory_vs_not_exposed == "Refractory" |
      carfilzomib_exposed_vs_refractory_vs_not_exposed == "Refractory"            ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(dara = case_when(
    daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed == "Refractory"            ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(doubleref = case_when(
    proteasome == "Yes" &
      immuno == "Yes"                                              ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(tripleref = case_when(
    proteasome == "Yes" &
      immuno == "Yes" &
      daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed == "Refractory"          ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(pentaref = case_when(
    bortezomib_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      carfilzomib_exposed_vs_refractory_vs_not_exposed == "Refractory" &
      lenalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      pomalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed == "Refractory"          ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(number_prior_lines_therapy = case_when(
    number_of_prior_lines_of_therapy <= 4                        ~ "≤ 4",
    number_of_prior_lines_of_therapy > 4                         ~ "> 4"
  ))
```

```{r Baseline labs}
cart1 <- cart %>% 
  # Baseline labs ----
  mutate(baseline_ferritin_cat = case_when(
    baseline_ferritin_pre_ld >= 400                                      ~ "≥ ULN at LD (≥ 400)",
    baseline_ferritin_pre_ld < 400                                       ~ "Normal (< 400)"
  ), baseline_ferritin_cat = 
    factor(baseline_ferritin_cat, levels = c("Normal (< 400)",
                                             "≥ ULN at LD (≥ 400)"))) %>% 
  mutate(baseline_crp_cat = case_when(
    baseline_crp_pre_ld  >= 0.5                                           ~ "≥ ULN at LD (≥ 0.5)",
    baseline_crp_pre_ld  < 0.5                                            ~ "Normal (< 0.5)"
  ), baseline_crp_cat = 
    factor(baseline_crp_cat, levels = c("Normal (< 0.5)",
                                        "≥ ULN at LD (≥ 0.5)"))) %>% 
  mutate(baseline_B2M = case_when(
    baseline_b2m_pre_ld >= 5.5                                    ~ "≥ 5.5",
    baseline_b2m_pre_ld < 5.5                                     ~ "< 5.5"
  )) %>%
  mutate(cart_cell_dose = case_when(
    cell_dose_million_cells >= 0.7                                ~ "≥ 0.7",
    cell_dose_million_cells < 0.7                                 ~ "< 0.7",
    TRUE                                                          ~ NA_character_
  ),cart_cell_dose = 
    factor(cart_cell_dose, levels = c("≥ 0.7", 
                                      "< 0.7"))) %>% 
  mutate(access_type = case_when(
    str_detect(access_type, "^C|catheter")                          ~ "Central venous catheter",
    str_detect(access_type, "^P")                                 ~ "Peripheral",
    TRUE                                                          ~ access_type
  ))
```

@@

    ORR_mon12 == "ORR"                                            ~ "ORR"

@@

@@

```{r delayed NT}
cilta <- cart6 %>%
  mutate(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no = case_when(
    is.na(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no) 
                                                                  ~ "No",
    TRUE           ~ other_delayed_non_parkinsonian_neurologic_toxicity_yes_no
  )) %>%
  mutate(parkinsonian_neurotoxicity_yes_no = case_when(
    parkinsonian_neurotoxicity_yes_no == "Yes" & 
      what_non_parkinsonian_neurotoxicity == "Bell's palsy"       ~ "No",
    is.na(parkinsonian_neurotoxicity_yes_no) ~ "No",
    TRUE ~ parkinsonian_neurotoxicity_yes_no
  )) %>%
  mutate(delayed_neuro = case_when(
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" |
      parkinsonian_neurotoxicity_yes_no == "Yes"                  ~ "Yes",
    TRUE                                                          ~ "No"
  )) %>%
  mutate(delayed_neuro_type = case_when(
    what_non_parkinsonian_neurotoxicity == "Aidp"                 ~ "Polyneuropathy",
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (PRES) and parkinsonism" 
                                                                  ~ "Parkinsonian/PRES",
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (pres); progressive multifocal leukoencephalopathy (pml)" 
                                                                  ~ "PRES/PML",
    parkinsonian_neurotoxicity_yes_no == "Yes"                    ~ "Parkinsonian",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsy")     ~ "Bell's palsy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsey")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "droop")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "PRES")    ~ "PRES", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "dysautonomia") 
                                                                 ~ "Dysautonomia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "plopia")    
                                                                  ~ "Diplopia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "Polyneuropathy") 
                                                                  ~ "Polyneuropathy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      is.na(what_non_parkinsonian_neurotoxicity)                  ~ "Unknown type",
    TRUE                                                          ~ what_non_parkinsonian_neurotoxicity
  )) 
```

```{r titers}
# Titers ----
cilta <- cilta %>% 
  mutate(ig_g_hsv1_2_apheresis = case_when(
    ig_g_hsv1_2_apheresis < 0.9         ~ "Negative",
    ig_g_hsv1_2_apheresis >= 0.9 &
      ig_g_hsv1_2_apheresis < 1.10      ~ "Indeterminate",
    ig_g_hsv1_2_apheresis >= 1.10       ~ "Positive"
  )) %>%
  mutate(ig_g_hsv1_2_d90 = case_when(
    ig_g_hsv1_2_d90 < 0.9         ~ "Negative",
    ig_g_hsv1_2_d90 >= 0.9 &
      ig_g_hsv1_2_d90 < 1.10      ~ "Indeterminate",
    ig_g_hsv1_2_d90 >= 1.10       ~ "Positive"
  )) %>%
  mutate_at(c("ig_g_hsv1_2_apheresis",
              "ig_g_hsv1_2_d90"),
            ~ factor(., levels = c("Positive", "Indeterminate", "Negative"))) %>%

@@

@@

                         cytogenetics = "High risk cytogenetics", 

@@

@@

>>>>

Characteristics <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "CHARACTERISTICS AND OUTCOMES ", skip = 1)
Counts <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "COUNTS")
Infections <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "INFECTIONS")
Support <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "SUPPORT")
Pneumo_titers <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "BACTERIAL AND VIRAL TITERS")
Apheresis <- 
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "APHERESIS")
id_to_modify_neurotox <- 
  read_csv(
    paste0(here(), 
           "/cilta_cel/patient id who had icans and delayed neurotox - need to change neurotox type to PRES.csv"))
```

@@

  mutate(across(where(is.character), ~ str_replace(., "Unknown|unknown", NA_character_))) %>%
  # Create site variable
  mutate(site = case_when(
    str_detect(pt_identifier, "MCC")               ~ "Moffitt",
    str_detect(pt_identifier, "CCT")               ~ "Stanford",
    str_detect(pt_identifier, "KUMC")              ~ "KUMC",
    str_detect(pt_identifier, "MDA")               ~ "MD Anderson?",
    str_detect(pt_identifier, "Utah")              ~ "Utah"
  )) %>%
  # Suboptimal is NA
  mutate(across(c(#"bm_plasma_cell_percent_at_pre_ld",
                  "high_marrow_burden_50_percent",
                  # contains("normo_hypo_hyper"),
                  contains("fibrosis"),
                  contains("dysplasia"),
                  "b2_microglobulin_day_180"), 
                ~ str_replace(., "Suboptimal", NA_character_))) %>%
  # Are numerical - also remove "Suboptimal"
  mutate(across(c(starts_with("marrow_fibrosis"),
                  starts_with("ldh_")
                  ), 
                ~ as.numeric(.))) %>%
  mutate(across(c("response_to_bridging_chemotherapy"), 
                ~ str_replace(., "Not evaluable", NA_character_))) %>% 
  # Convert 0/1 to No/Yes
  mutate_at(c("infection_yes_1_no_0",
              "severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0",
              # "bm_plasma_cell_percent_at_pre_ld",
              # "high_marrow_burden_50_percent",
              # "ECOG > or = 2? (Yes, No)",
              # deletion_17p_prior_to_car_t_infusion_yes_no,
              # "t_4_14_prior_to_car_t_infusion_yes_no",
              # "t_14_16_prior_to_car_t_infusion_yes_no",
              # "steroid_use_yes_no", "tocilizumab_yes_no", "anakinra_yes_no",
              # "Bridging Therapy (Yes=1, No=0)",
              # "Received alkylating therapy with bridging (Yes=1, No=0)",
              "need_for_g_csf_post_infus_yes_1_no_0",
              "need_for_ivig_yes_1_no_0",
              "cd34_stem_cell_boost_yes_1_no_0",
              "rbc_transfusion_within_30d_post_cart_yes_1_no_0", "plt_transfusion_within_30d_post_cart_yes_1_no_0", 
              "rbc_transfusion_30d_post_cart_yes_1_no_0", "plt_transfusion_30d_post_cart_yes_1_no_0",
              "tpo_agonist_post_cart_yes_1_no_0"), 
            ~ case_when(
              . == 1                                              ~ "Yes",
              . == 0                                              ~ "No",
              TRUE                                                ~ NA_character_
            )) %>% 
  # Marrow ----
  mutate(marrow_cellularity_baseline_normo_hypo_hyper = case_when(
    marrow_cellularity_baseline_normo_hypo_hyper == "\"patchy\""                 ~ "hyper",
    TRUE                                                          ~ marrow_cellularity_baseline_normo_hypo_hyper
  )) %>%
  mutate(marrow_cellularity_day_30_normo_hypo_hyper = case_when(
    marrow_cellularity_day_30_normo_hypo_hyper == "aplastic"                    ~ "hypo",
    TRUE                                                          ~ marrow_cellularity_day_30_normo_hypo_hyper
  )) %>%
  # Separate variable cellularity
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Variable"                         ~ "Yes"
  ), .names = "is_variable_{.col}")) %>% 
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Pauci"                            ~ "Hypo",
    . == "Variable"                         ~ NA_character_,
    TRUE                                    ~ .
  ))) %>%

@@

  # Myeloma
  mutate(oligo_or_non_secretory = case_when(
    oligo_or_non_secretory == "Non-Secretory" ~ "Yes",
    oligo_or_non_secretory == "Oligosecretory" ~ "Yes",
    oligo_or_non_secretory == "Unknown" ~ NA_character_,
    TRUE ~ oligo_or_non_secretory
  # mutate(oligo_or_non_secretory_yes_no = case_when( # is "oligo_or_non_secretory_yes_no" now
  #   `Yes, Oligo or Yes, Non-Secretory` == "Non-Secretory" ~ "Yes",
  #   `Yes, Oligo or Yes, Non-Secretory` == "Oligosecretory" ~ "Yes",
  #   `Yes, Oligo or Yes, Non-Secretory` == "Oligo-secretory" ~ "Yes",
  #   TRUE ~ `Yes, Oligo or Yes, Non-Secretory`
  mutate(subtype = case_when(
    oligo_or_non_secretory_yes_no == "Yes" ~ "Oligo/non-secretory",
    myeloma_involved_heavy_chain == "None (Light Chain Restricted)" | 
     myeloma_involved_light_chain == "Lambda" & 
      is.na(myeloma_involved_heavy_chain) ~ "Light chain only",
    myeloma_involved_heavy_chain != "None (Light Chain Restricted)" 
                   ~ "Intact immunoglobulin (Heavy + Light)",
  # Cytogenetics ----
  mutate(cytogenetics = case_when(
    deletion_17p_prior_to_car_t_infusion_yes_no == "Yes" | 
      t_4_14_prior_to_car_t_infusion_yes_no == "Yes" | 
      t_14_16_prior_to_car_t_infusion_yes_no == "Yes"             ~ "Yes",
    deletion_17p_prior_to_car_t_infusion_yes_no == "No" &
      t_4_14_prior_to_car_t_infusion_yes_no == "No" &
      t_14_16_prior_to_car_t_infusion_yes_no == "No"               ~ "No",
  mutate(gain_amp1q21 = case_when(
    gain_amp1q21 == "No"                                           ~ "No",
    !is.na(gain_amp1q21)                                           ~ "Yes"
  # Refractory status ----
  mutate(lenalidomide_exposed_vs_refractory_vs_not_exposed = case_when(
    str_detect(
      lenalidomide_exposed_vs_refractory_vs_not_exposed, "Ref")     ~ "Refractory",
    TRUE           ~ lenalidomide_exposed_vs_refractory_vs_not_exposed
  mutate(immuno = case_when(
    lenalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" |
      pomalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory"           ~ "Yes",
  mutate(proteasome = case_when(
    bortezomib_exposed_vs_refractory_vs_not_exposed == "Refractory" |
      carfilzomib_exposed_vs_refractory_vs_not_exposed == "Refractory"            ~ "Yes",
  mutate(dara = case_when(
    daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed == "Refractory"            ~ "Yes",
  mutate(doubleref = case_when(
    proteasome == "Yes" &
      immuno == "Yes"                                              ~ "Yes",
  mutate(tripleref = case_when(
    proteasome == "Yes" &
      immuno == "Yes" &
      daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed == "Refractory"          ~ "Yes",
  mutate(pentaref = case_when(
    bortezomib_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      carfilzomib_exposed_vs_refractory_vs_not_exposed == "Refractory" &
      lenalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      pomalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed == "Refractory"          ~ "Yes",
  mutate(number_prior_lines_therapy = case_when(
    number_of_prior_lines_of_therapy <= 4                        ~ "≤ 4",
    number_of_prior_lines_of_therapy > 4                         ~ "> 4"

```{r Baseline labs}
cart1 <- cart %>% 
  # Baseline labs ----
  mutate(baseline_ferritin_cat = case_when(
    baseline_ferritin_pre_ld >= 400                                      ~ "≥ ULN at LD (≥ 400)",
    baseline_ferritin_pre_ld < 400                                       ~ "Normal (< 400)"
  ), baseline_ferritin_cat = 
    factor(baseline_ferritin_cat, levels = c("Normal (< 400)",
                                             "≥ ULN at LD (≥ 400)"))) %>% 
  mutate(baseline_crp_cat = case_when(
    baseline_crp_pre_ld  >= 0.5                                           ~ "≥ ULN at LD (≥ 0.5)",
    baseline_crp_pre_ld  < 0.5                                            ~ "Normal (< 0.5)"
  ), baseline_crp_cat = 
    factor(baseline_crp_cat, levels = c("Normal (< 0.5)",
                                        "≥ ULN at LD (≥ 0.5)"))) %>% 
  mutate(baseline_B2M = case_when(
    baseline_b2m_pre_ld >= 5.5                                    ~ "≥ 5.5",
    baseline_b2m_pre_ld < 5.5                                     ~ "< 5.5"
  mutate(cart_cell_dose = case_when(
    cell_dose_million_cells >= 0.7                                ~ "≥ 0.7",
    cell_dose_million_cells < 0.7                                 ~ "< 0.7",
  ),cart_cell_dose = 
    factor(cart_cell_dose, levels = c("≥ 0.7", 
                                      "< 0.7"))) %>% 
  mutate(access_type = case_when(
    str_detect(access_type, "^C|catheter")                        ~ "Central venous catheter",
    str_detect(access_type, "^P")                                 ~ "Peripheral",
    TRUE                                                          ~ access_type
  # Supportive therapies and neutrophil recovery----
  mutate(neutrophil_recovery_ANC_never_below_500 = case_when(
    day_of_neutrophil_recovery == "Anc never <500"               ~ "Yes",
    day_of_neutrophil_recovery == "No neutropenia"               ~ "Yes"
  mutate(neutrophil_recovery_did_not_recover = case_when(
    day_of_neutrophil_recovery == "Deceased"                     ~ "Yes",
    day_of_neutrophil_recovery == "Pd prior to anc recovery"     ~ "Yes"
  mutate(day_of_neutrophil_recovery_ = case_when(
    site == "KUMC"                                               ~ as.numeric(day_of_neutrophil_recovery)
  mutate(across(c("last_date_of_gcsf", "day_of_neutrophil_recovery",
                  "last_date_of_ivig"), 
         ~ as.Date(as.numeric(.), origin = "1899-12-30"))) %>% 
  mutate(first_day_of_gcsf = interval(
             start = date_of_car_t_infusion, 
             end = first_date_of_gcsf)/
           duration(n=1, units = "days"
  mutate(last_day_of_gcsf = interval(
             start = date_of_car_t_infusion, 
             end = last_date_of_gcsf)/
           duration(n=1, units = "days"
  mutate(day_of_stem_cell_boost = interval(
             start = date_of_car_t_infusion, 
             end = date_of_stem_cell_boost)/
           duration(n=1, units = "days"
  mutate(day_of_neutrophil_recovery = interval(
             start = date_of_car_t_infusion, 
             end = day_of_neutrophil_recovery)/
           duration(n=1, units = "days"
  ), day_of_neutrophil_recovery = coalesce(day_of_neutrophil_recovery_, day_of_neutrophil_recovery)) %>% 
  select(-day_of_neutrophil_recovery_) %>% 
  mutate(transfusion_postCART = case_when(
    rbc_transfusion_within_30d_post_cart_yes_1_no_0 == "Yes" |
      plt_transfusion_within_30d_post_cart_yes_1_no_0 == "Yes" |
      rbc_transfusion_30d_post_cart_yes_1_no_0 == "Yes" |
      plt_transfusion_30d_post_cart_yes_1_no_0 == "Yes"              ~ "Yes"
  mutate(first_day_of_tpo_agonist = interval(
             start = date_of_car_t_infusion, 
             end = first_date_of_tpo_agonist)/
           duration(n=1, units = "days"
  mutate(last_day_of_tpo_agonist = interval(
             start = date_of_car_t_infusion, 
             end = last_date_of_tpo_agonist)/
           duration(n=1, units = "days"
  mutate(first_day_of_ivig = interval(
             start = date_of_car_t_infusion, 
             end = first_date_of_ivig)/
           duration(n=1, units = "days"
  mutate(last_day_of_ivig = interval(
             start = date_of_car_t_infusion, 
             end = last_date_of_ivig)/
           duration(n=1, units = "days"

@@

    ORR_mon12 == "ORR"                                            ~ "ORR",
    is.na(ORR_30days) & 
      is.na(ORR_mon3) & 
      is.na(ORR_mon6) & 
      is.na(ORR_mon9) &
      is.na(ORR_mon12)                                            ~ NA_character_, 
     TRUE                                                         ~ "SD/PD"

@@

  mutate(best_ORRcollapsed = case_when(
    str_detect(best_response, "CR|PR")                            ~ "PR or better", 
    str_detect(best_response, "SD|PD")                            ~ "< PR",

@@

```{r delayed NT}
cilta <- cart6 %>%
  mutate(what_non_parkinsonian_neurotoxicity = case_when(
    what_non_parkinsonian_neurotoxicity == "Delayed icans, hippocampal sclerosis/gliosis"
                                                                  ~ "cerebral edema/PRES",
    TRUE                                                          ~ what_non_parkinsonian_neurotoxicity
  )) %>% 
  mutate(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no = case_when(
    is.na(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no) 
                                                                  ~ "No",
    TRUE           ~ other_delayed_non_parkinsonian_neurologic_toxicity_yes_no
  )) %>%
  mutate(parkinsonian_neurotoxicity_yes_no = case_when(
    str_detect(pt_identifier, id_to_modify_neurotox$id)           ~ "No",
    parkinsonian_neurotoxicity_yes_no == "Yes" & 
      what_non_parkinsonian_neurotoxicity == "Bell's palsy"       ~ "No",
    is.na(parkinsonian_neurotoxicity_yes_no)                      ~ "No",
    TRUE                                                          ~ parkinsonian_neurotoxicity_yes_no
  )) %>%
  mutate(delayed_neuro = case_when(
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" |
      parkinsonian_neurotoxicity_yes_no == "Yes"                  ~ "Yes",
    TRUE                                                          ~ "No"
  )) %>%
  mutate(delayed_neuro_type = case_when(
    str_detect(pt_identifier, id_to_modify_neurotox$id)           ~ "PRES",
    what_non_parkinsonian_neurotoxicity == "cerebral edema/PRES"
                                                                  ~ "PRES",
    what_non_parkinsonian_neurotoxicity == "Aidp"                 ~ "Polyneuropathy",
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (pres) and parkinsonism" 
                                                                  ~ "Parkinsonian/PRES",
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (pres); progressive multifocal leukoencephalopathy (pml)" 
                                                                  ~ "PRES/PML",
    parkinsonian_neurotoxicity_yes_no == "Yes"                    ~ "Parkinsonian",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsy")     ~ "Bell's palsy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsey")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "droop")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "PRES")    ~ "PRES", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "dysautonomia") 
                                                                 ~ "Dysautonomia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "plopia")    
                                                                  ~ "Diplopia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "Polyneuropathy") 
                                                                  ~ "Polyneuropathy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      is.na(what_non_parkinsonian_neurotoxicity)                  ~ "Unknown type",
    TRUE                                                          ~ what_non_parkinsonian_neurotoxicity
  )) 
```

```{r titers}
# Titers ----
cilta <- cilta %>% 
  mutate(across(c(starts_with("ig_g_hsv1_2")), ~ case_when(
    . < 0.9         ~ "Negative",
    . >= 0.9 &
      . < 1.10      ~ "Indeterminate",
    . >= 1.10       ~ "Positive"
  ))) %>%

  # mutate(ig_g_hsv1_2_apheresis = case_when(
  #   ig_g_hsv1_2_apheresis < 0.9         ~ "Negative",
  #   ig_g_hsv1_2_apheresis >= 0.9 &
  #     ig_g_hsv1_2_apheresis < 1.10      ~ "Indeterminate",
  #   ig_g_hsv1_2_apheresis >= 1.10       ~ "Positive"
  # )) %>%
  # mutate(ig_g_hsv1_2_d90 = case_when(
  #   ig_g_hsv1_2_d90 < 0.9         ~ "Negative",
  #   ig_g_hsv1_2_d90 >= 0.9 &
  #     ig_g_hsv1_2_d90 < 1.10      ~ "Indeterminate",
  #   ig_g_hsv1_2_d90 >= 1.10       ~ "Positive"
  # )) %>%
  # mutate(ig_g_hsv1_2_d180 = case_when(
  #   ig_g_hsv1_2_d180 < 0.9         ~ "Negative",
  #   ig_g_hsv1_2_d180 >= 0.9 &
  #     ig_g_hsv1_2_d180 < 1.10      ~ "Indeterminate",
  #   ig_g_hsv1_2_d180 >= 1.10       ~ "Positive"
  # )) %>%
  mutate_at(c("ig_g_hsv1_2_apheresis",
              "ig_g_hsv1_2_d90",
              "ig_g_hsv1_2_d180"),
            ~ factor(., levels = c("Positive", "Indeterminate", "Negative"))) %>%

@@

                         os_from_infusion_months = "Follow-up time from infusion (months)",

@@

                         cytogenetics = "High risk cytogenetics (not include gain 1q)", 

@@

                         gain_amp1q21 = "Gain/amp 1q21",

@@

                         day_of_neutrophil_recovery = "Day of neutrophil recovery",
                         transfusion_postCART = "Transfusion post-CAR T",
